oauthlib
========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.com/sckott/oauthlib.svg?branch=master)](https://travis-ci.com/sckott/oauthlib)

oauthlib: build and validate OAuth headers, following Ruby's <https://github.com/laserlemon/simple_oauth>

**BEWARE: VERY ALPHA - & NOT FUNCTIONAL YET**

## Installation

```{r eval=FALSE}
remotes::install_github("sckott/oauthlib")
```

```{r}
library("oauthlib")
```

## example

```{r}
(x <- OAuth$new("get", "https://api.twitter.com/1/statuses/friends.json", list()))
x
x$url()
x$as_string()
x$signed_attributes()
```

## Meta

* Please [report any issues or bugs](https://github.com/sckott/oauthlib/issues).
* License: MIT
* Get citation information for `oauthlib` in R doing `citation(package = 'oauthlib')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

